The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-10-11 article.tex
Fix reviewer comments.

  Previous versions of the API represented stereochemistry in different ways, this hindered
  interconversion between and within file 
  .formats. CDK \cdkversion{} standardizes
  upon a new core representation and procedures have been updated or added to
  enable duplicate checking, pattern matching, and interconversion.

@@

The most significant functional change here is that the SMILES parser automatically 
locates the positions of double bonds in de-localised aromatic systems (Kekulisation).
If this invariant can not be meet the SMILES is rejected as invalid. It is 
possible to override this check but this is strongly discouraged as rejected
molecules do not have a fixed formula or tautomer.

@@

Support for ChemAxon Extended SMILES (CXSMILES)\cite{CXSMILES} layers has been added
to the CDK \cdkversion{}. CXSMILES provides a powerful means of including auxiliary 
information in a SMILES string such as 2D/3D coordinates, atom values, generic labels, 
repeat units, and positional variation. CXSMILES is achieving by placing additional
information between pipe characters (`\texttt{|}') in the SMILES title field. Information
is annotated based on the order of the atoms in the SMILES string. An example CXSMILES
for a generic structure is shown below.

>>>>

  Previous versions of the API represented stereochemistry in different ways, this hindered
  interconversion between and within file formats CDK \cdkversion{} standardizes
  upon a new core representation and procedures have been updated or added to
  enable duplicate checking, pattern matching, and interconversion.

@@

The most significant functional change here is that the SMILES parser automatically 
locates the positions of double bonds in de-localised aromatic systems (Kekulisation).
If this invariant cannot be met the SMILES is rejected as invalid. It is 
possible to override this check but this is strongly discouraged as rejected
molecules do not have a fixed formula or tautomer.

@@

Support for ChemAxon Extended SMILES (CXSMILES)\cite{CXSMILES} layers has been added
to CDK \cdkversion{}. CXSMILES provides a powerful means of including auxiliary 
information in a SMILES string such as 2D/3D coordinates, atom values, generic labels, 
repeat units, and positional variation. CXSMILES is achieving by placing additional
information between pipe characters (`\texttt{|}') in the SMILES title field. Information
is annotated based on the order of the atoms in the SMILES string. An example CXSMILES
for a generic structure is shown below.
